Competing Bandits: \\ The Perils of Exploration under Competition

### 2018-11-06 paper/content/model.tex
Some edits in the model.

\xhdr{Agents.}
\gaedit{For simplicity we suppose that firms compete for agents on a single dimension, quality, that is summarized via the rewards experienced by past consumers.\footnote{One can think that there are two quality types - a reward of 1 is a high type and a reward of 0 is a low type}} Agents are myopic and non-strategic: they choose among the firms so as to maximize their expected reward \gaedit{(i.e. select the firm with the highest quality)}, without attempting to influence the firms' learning algorithms or rewards of the future users. Agents are not well-informed: they only receive a rough signal about each firm's performance before they choose a firm, and no other information.

Concretely, each firm has a \emph{reputation score}, and each agent's choice is driven by these two numbers. We posit a version of rational behavior: each agent chooses a firm with a maximal reputation score (breaking ties uniformly). The reputation score is simply a sliding window average: an average reward of the last $M$ agents that chose this firm.\gaedit{\footnote{One can think of this as similar to ratings aggregations on many online platforms such as Yelp, Tripadvisor, etc.}}

@@

For concreteness, we fix one algorithm from each class. Our pilot experiments indicate that the results do not change substantially if other algorithms are chosen. \gaedit{We make this restriction since we are mainly interested in qualitative differences between standard ``good" multi-armed bandit algorithms and what algorithms are incentivized in competition.} For technical reasons, we consider Bayesian versions initialized with a ``fake" prior (\ie not based on actual knowledge). We consider:

>>>>

\xhdr{Agents.}
\gaedit{For simplicity we suppose that firms compete for agents on a single dimension, quality, that is summarized via the rewards experienced by past consumers.
\OMIT{\footnote{One can think that there are two quality types - a reward of 1 is a high type and a reward of 0 is a low type}}}
Agents are myopic and non-strategic: they \asedit{would like} to choose among the firms so as to maximize their expected reward \gaedit{(i.e. select the firm with the highest quality)}, without attempting to influence the firms' learning algorithms or rewards of the future users. Agents are not well-informed: they only receive a rough signal about each firm's performance before they choose a firm, and no other information.

Concretely, each of the two firms has a \emph{reputation score}, and each agent's choice is driven by these two numbers. We posit a version of rational behavior: each agent chooses a firm with a maximal reputation score (breaking ties uniformly). The reputation score is simply a sliding window average: an average reward of the last $M$ agents that chose this firm. \asedit{This is similar to ratings aggregators on many online platforms such as Yelp, Tripadvisor, etc.).}

@@

\asedit{We are mainly interested in qualitative differences between the three classes.} For concreteness, we fix one algorithm from each class. Our pilot experiments indicate that our findings do not change substantially if other algorithms are chosen. For technical reasons, we consider Bayesian versions initialized with a ``fake" prior (\ie not based on actual knowledge). We consider:
